Supplemental Material for: The evolution of gene expression in the term placenta of viviparous mammals

### 2015-10-19 manuscript/supplemental_material.Rnw
output all expression tables in supplemental materials output all go tables in supplemental materials

@@

@@

<<human.expressed.genes,echo=FALSE,results="asis">>=
print(xtable(genes.expression.table(species.name="homo sapiens"),
             caption="Expression of all genes with FPKM $\\ge 50$ in \\textit{Homo sapiens}",
             label="tab:all_human_placenta"
             ),
      booktabs=TRUE,
      tabular.environment="longtable",
      floating=FALSE,
      caption.placement="top",
      add.to.row = list(pos = list(0),command = "\\midrule \\endhead "),
      size="\\tiny"
      )
@

>>>>

<<load.go.results,echo=FALSE,results="hide",cache.extra=tools::md5sum("../go_annotation/go_tissue_analysis")>>=
load("../go_annotation/go_tissue_analysis")

@@

<<go.analysis.all.species,echo=FALSE,results="asis">>=
for (this.species in go.results[grepl("100 No Housekeeping",type) & FDR <= 0.0005,unique(species)]) {
    print(xtable(go.results[grepl("100 No Housekeeping",type) & FDR <= 0.0005 & species == this.species,
                            list(GO.ID,Term,FDR,Ontology,type)
                            ],
                 caption=paste0("Signficantly enriched ($\\mathrm{FDR}\\le0.0005$) GO terms in ",
                     "\\textit{",capfirst(this.species),"}"),
                 label=paste0("tab:go_terms_enriched_",gsub(" ","_",this.species)),
                 display=c("s","s","s","e","s","s")
                 ),
          size="\\small",
          booktabs=TRUE,
          floating=TRUE)
}
@

@@

<<top.expressed.genes,echo=FALSE,results="asis">>=
for (this.species in combined.fpkm[,sort(unique(species))]) {
    print(xtable(genes.expression.table(species.name=this.species),
                 caption=paste0("Expression of all genes with FPKM $\\ge 50$ in \\textit{",
                     capfirst(this.species),"}"),
                 label=paste0("tab:all_",gsub(" ","_",this.species),"_placenta")
                 ),
          booktabs=TRUE,
          tabular.environment="longtable",
          floating=FALSE,
          caption.placement="top",
          add.to.row = list(pos = list(0),command = "\\midrule \\endhead "),
          size="\\tiny"
          )
}
@
